---
title: "Developing data products week3"
author: "Osiepere"
date: "2019 M01 25"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

World Cities Map
The map shows a map of the world cities. The data was taken from https://simplemaps.com/data/world-cities

library(leaflet)

## Slide with R Output

```{r}
df <- read.csv("worldcities.csv")
df %>% leaflet() %>%
  addTiles() %>%
  addMarkers(
    lat = df$lat, 
    lng = df$lng, 
    popup = paste(df$popup, "<br>", "City:", df$city_ascii),
    clusterOptions = markerClusterOptions())
```

## Slide with Plot

```{r}
```

